\textsf{Are frontier models superhuman chemists?}

### 2024-03-19 src/tex/appendix.tex
correlate reading ease with performance
update reading ease figure

>>>>

\begin{figure}
    \centering
    \includegraphics{figures/reading_ease_vs_model_performance.pdf}
    \caption{\textbf{Model performance as a function of reading ease.} The violinplots show the distribution of reading ease scores for questions that were answered completely correctly and those that were not. We do not observe a clear correlation between the reading ease of the questions and the performance of the models. }
    \script{reading_ease_vs_model_performance.py}
\end{figure}
